\begin{abstract}
Text-conditioned image generation has gained significant attention in recent years and is processing increasingly longer and comprehensive text prompts. 
In everyday life, dense and intricate text appears in contexts like advertisements, infographics, and signage, where the integration of both text and visuals is essential for conveying complex information. 
However, despite these advances, the rendering of images containing long-form text remains a persistent challenge, largely due to the limitations of existing datasets, which often focus on shorter and simpler text. 
To address this gap, we introduce \DatasetName, a novel dataset specifically designed to evaluate \emph{long-text rendering}, where ``long text'' refers not only to textual length but also to layout complexity and semantic richness. 
In our context, long text involves dense visual content, hierarchical structures, and interleaved text-image layouts, as exemplified by subsets like \textit{TextVisionBlend}, \textit{PPT2Structured}, \textit{CoverBook}, and \textit{TextScenesHQ}. 
Our dataset consists of 5 million generated and collected images across diverse data types, enabling comprehensive evaluation of large-scale generative models on long-text image generation. 
We further curate 4,000 human-improved test cases (\EvalDatasetName) across 4 domains, establishing one of the most extensive benchmarks for text rendering. 
Evaluations suggest that \EvalDatasetName presents significant challenges even for the most advanced proprietary models (e.g., GPT4o), while open-source counterparts show an even larger performance gap. 
Notably, diffusion and autoregressive models with weak text rendering improve substantially after training on our dataset.
These findings position \DatasetName as a valuable resource for training and evaluating next-generation text-conditioned image generation models. 
\end{abstract}

% \begin{abstract}
% Text-conditioned image generation has gained significant attention in recent years and is processing increasingly longer and comprehensive text prompts. 
% In everyday life, dense and intricate text appears in contexts like advertisements, infographics, and signage, where the integration of both text and visuals is essential for conveying complex information. 
% However, despite these advances, the rendering of images containing long-form text remains a persistent challenge, largely due to the limitations of existing datasets, which often focus on shorter and simpler text. 
% To address this gap, we introduce \DatasetName, a novel dataset specifically designed to evaluate long-text rendering in text-conditioned image generation.
% Our dataset consists of 5 million long-text generated and collected images across diverse data types, enabling comprehensive evaluation of large-scale generative models on long-text image generation. 
% We further curate 4000 human-improved test set \EvalDatasetName~ across 4 data domains, establishing one of the most extensive benchmarks for text rendering.
% Evaluations suggest that the \EvalDatasetName benchmarks present significant challenges even for the most advanced proprietary models (e.g., GPT4o), while their open-source counterparts show an even larger performance gap.
% These evidences position \DatasetName as a valuable dataset for training and evaluating future-generation text-conditioned image generation models.
% Notably, models with poor initial text rendering capabilities exhibit significant improvements after being further trained on our dataset.
% %Datasets are released in \url{https://textatlas5m.github.io}.
% \end{abstract}